Approximation as Differentiation

### 2025-06-28 main/first-order.tex
Drop inductive types from syntax, in favour of lists.

To interpret the syntactic type constructor $\synVar{L}$, consider the strong monad $(\mathcal{L}, \eta, \mu)$
which acts on posets $X$ to extend them with a distinguished bottom element $\bot$ and which acts on monotone
functions $f$ between posets to extend them with a mapping from $\bot$ to $\bot$. $\mathcal{L}$ is also a
strong monad on meet-semilattices. On (bounded) join-semilattices, $\mathcal{L}$ induces a costrong comonad
$(\mathcal{L}, \varepsilon, \delta)$, with the bottom element of $X$ needed to implement the counit
$\varepsilon_X: \mathcal{L}(X) \to X$. These two combine to form a strong lifting monad in $\LatGal$ with unit
$\varepsilon_X \dashv \eta_X$ and multiplication $\delta_X \dashv \mu_X$.

>>>>

To interpret the syntactic type constructor $\synVar{L}$, consider the strong monad $(\mathcal{L}, \eta, \mu)$
which acts on a poset $X$ to extend it with a distinguished bottom element $\bot$ and which acts on a monotone
function $f$ between posets to extend it with a mapping from $\bot$ to $\bot$. $\mathcal{L}$ is also a strong
monad on meet-semilattices. On (bounded) join-semilattices, $\mathcal{L}$ induces a costrong comonad
$(\mathcal{L}, \varepsilon, \delta)$, with the bottom element of $X$ needed to implement the counit
$\varepsilon_X: \mathcal{L}(X) \to X$. These two combine to form a strong lifting monad in $\LatGal$ with unit
$\varepsilon_X \dashv \eta_X$ and multiplication $\delta_X \dashv \mu_X$.

### 2025-06-28 main/language.tex
Drop inductive types from syntax, in favour of lists.

We introduce a total higher-order functional language with a (reasonably) expressive type
system~\cite{crole94,pitts01,santocanale02}, over a set $\PrimTy$ of primitive types $\rho$ and sets
$\PrimOp^\rho_{\rho_1,\ldots,\rho_n}$ of primitive operations $\phi$.

>>>>

We introduce a total higher-order functional language, over a set $\PrimTy$ of primitive types $\rho$ and sets
$\PrimOp^\rho_{\rho_1,\ldots,\rho_n}$ of primitive operations $\phi$, equipped with sums, products, functions
and a data type of lists. We omit a treatment of general inductive or coinductive types.
